## 續(篩選飲食上傳>80%) {#strat_1_ob_filtered}

**依據減重成效進行分層分析，分成三個組別：**

-   **成效「優異」: (減重\>10%)**
-   **「良好」: (減重介於 5 \~ 10%)**
-   **「低於預期」: (減重\< 3%)**

```{r  paged.print=TRUE}
table_01_exclude_record_factor
```

### 初始狀態(Baseline) {#baseline_ob_filtered .unnumbered}



#### Inbody {#baseline_ob_filtered_inbody .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_1") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_1")],
          ncol = 2,
          labels = paste0(LETTERS[1], seq(1,100)))
```

#### 相位角 {#baseline_ob_filtered_wepa .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_2") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_2")],
          ncol = 2,
          labels = paste0(LETTERS[1], seq(which(myplot_table_global_filter[["block"]] == "t0_2") %>% min(),1000)))
```

#### 體水份 {#baseline_ob_filtered_water .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_3") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_3")],
          ncol = 2,
          labels = paste0(LETTERS[1], seq(which(myplot_table_global_filter[["block"]] == "t0_3") %>% min(),1000)))
```

#### inbody - 部位別 {#baseline_ob_filtered_inbody_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_4") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_4")],
          ncol = 2,
          labels = paste0(LETTERS[1], seq(which(myplot_table_global_filter[["block"]] == "t0_4") %>% min(),1000)))
```

#### 體水份 - 部位別 {#baseline_ob_filtered_water_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_5") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_5")],
          ncol = 2,
          labels = paste0(LETTERS[1], seq(which(myplot_table_global_filter[["block"]] == "t0_5") %>% min(),1000)))
```

#### Glucose/Insulin {#baseline_ob_filtered_gi .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_6") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_6")],
          ncol = 2,
          labels = paste0(LETTERS[2], seq(which(myplot_table_global_filter[["block"]] == "t0_6") %>% min(),1000)))
```

#### Lipid {#baseline_ob_filtered_lipid .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_7") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_7")],
          ncol = 2,
          labels = paste0(LETTERS[2], seq(which(myplot_table_global_filter[["block"]] == "t0_7") %>% min(),1000)))
```

#### Kidney {#baseline_ob_filtered_kidney .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_8") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_8")],
          ncol = 2,
          labels = paste0(LETTERS[2], seq(which(myplot_table_global_filter[["block"]] == "t0_8") %>% min(),1000)))
```

#### Hormone {#baseline_ob_filtered_hormone .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_9") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_9")],
          ncol = 2,
          labels = paste0(LETTERS[2], seq(which(myplot_table_global_filter[["block"]] == "t0_9") %>% min(),1000)))
```

#### Hematology {#baseline_ob_filtered_hematology .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t0_10") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t0_10")],
          ncol = 2,
          labels = paste0(LETTERS[2], seq(which(myplot_table_global_filter[["block"]] == "t0_10") %>% min(),1000)))
```

### 介入後狀態(Endpoint) {#endpoint_ob_filtered .unnumbered}

#### Inbody {#endpoint_ob_filtered_inbody .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_1") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_1")],
          ncol = 2,
          labels = paste0(LETTERS[3], seq(1,100)))
```

#### 相位角 {#endpoint_ob_filtered_wepa .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_2") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_2")],
          ncol = 2,
          labels = paste0(LETTERS[3], seq(which(myplot_table_global_filter[["block"]] == "t0_2") %>% min(),1000)))
```

#### 體水份 {#endpoint_ob_filtered_water .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_3") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_3")],
          ncol = 2,
          labels = paste0(LETTERS[3], seq(which(myplot_table_global_filter[["block"]] == "t0_3") %>% min(),1000)))
```

#### inbody - 部位別 {#endpoint_ob_filtered_inbody_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_4") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_4")],
          ncol = 2,
          labels = paste0(LETTERS[3], seq(which(myplot_table_global_filter[["block"]] == "t0_4") %>% min(),1000)))
```

#### 體水份 - 部位別 {#endpoint_ob_filtered_water_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_5") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_5")],
          ncol = 2,
          labels = paste0(LETTERS[3], seq(which(myplot_table_global_filter[["block"]] == "t0_5") %>% min(),1000)))
```

#### Glucose/Insulin {#endpoint_ob_filtered_gi .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_6") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_6")],
          ncol = 2,
          labels = paste0(LETTERS[4], seq(which(myplot_table_global_filter[["block"]] == "t0_6") %>% min(),1000)))
```

#### Lipid {#endpoint_ob_filtered_lipid .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_7") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_7")],
          ncol = 2,
          labels = paste0(LETTERS[4], seq(which(myplot_table_global_filter[["block"]] == "t0_7") %>% min(),1000)))
```

#### Kidney {#endpoint_ob_filtered_kidney .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_8") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_8")],
          ncol = 2,
          labels = paste0(LETTERS[4], seq(which(myplot_table_global_filter[["block"]] == "t0_8") %>% min(),1000)))
```

#### Hormone {#endpoint_ob_filtered_hormone .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_9") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_9")],
          ncol = 2,
          labels = paste0(LETTERS[4], seq(which(myplot_table_global_filter[["block"]] == "t0_9") %>% min(),1000)))
```

#### Hematology {#endpoint_ob_filtered_hematology .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "t1_10") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "t1_10")],
          ncol = 2,
          labels = paste0(LETTERS[4], seq(which(myplot_table_global_filter[["block"]] == "t0_10") %>% min(),1000)))
```

### 飲食(Diet) {#diet_ob_filtered .unnumbered}



```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "diet") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "diet")],
          ncol = 2,
          labels = paste0(LETTERS[5], seq(1,100)))
```

### ∆成效(Effectiveness) {#delta_ob_filtered .unnumbered}

#### Inbody {#delta_ob_filtered_inbody .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_1") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_1")],
          ncol = 2,
          labels = paste0(LETTERS[6], seq(1,100)))
```

#### 相位角 {#delta_ob_filtered_wepa .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_2") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_2")],
          ncol = 2,
          labels = paste0(LETTERS[6], seq(which(myplot_table_global_filter[["block"]] == "t0_2") %>% min(),1000)))
```

#### 體水份 {#delta_ob_filtered_water .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_3") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_3")],
          ncol = 2,
          labels = paste0(LETTERS[6], seq(which(myplot_table_global_filter[["block"]] == "t0_3") %>% min(),1000)))
```

#### inbody - 部位別 {#delta_ob_filtered_inbody_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_4") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_4")],
          ncol = 2,
          labels = paste0(LETTERS[6], seq(which(myplot_table_global_filter[["block"]] == "t0_4") %>% min(),1000)))
```

#### 體水份 - 部位別 {#delta_ob_filtered_water_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_5") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_5")],
          ncol = 2,
          labels = paste0(LETTERS[6], seq(which(myplot_table_global_filter[["block"]] == "t0_5") %>% min(),1000)))
```

#### Glucose/Insulin {#delta_ob_filtered_gi .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_6") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_6")],
          ncol = 2,
          labels = paste0(LETTERS[7], seq(which(myplot_table_global_filter[["block"]] == "t0_6") %>% min(),1000)))
```

#### Lipid {#delta_ob_filtered_lipid .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_7") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_7")],
          ncol = 2,
          labels = paste0(LETTERS[7], seq(which(myplot_table_global_filter[["block"]] == "t0_7") %>% min(),1000)))
```

#### Kidney {#delta_ob_filtered_kidney .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_8") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_8")],
          ncol = 2,
          labels = paste0(LETTERS[7], seq(which(myplot_table_global_filter[["block"]] == "t0_8") %>% min(),1000)))
```

#### Hormone {#delta_ob_filtered_hormone .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_9") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_9")],
          ncol = 2,
          labels = paste0(LETTERS[7], seq(which(myplot_table_global_filter[["block"]] == "t0_9") %>% min(),1000)))
```

#### Hematology {#delta_ob_filtered_hematology .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_10") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_10")],
          ncol = 2,
          labels = paste0(LETTERS[7], seq(which(myplot_table_global_filter[["block"]] == "t0_10") %>% min(),1000)))
```

### ∆成效(%)(Effectiveness) {#delta_p_ob_filtered .unnumbered}

#### Inbody {#delta_p_ob_filtered_inbody .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_1") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_1")],
          ncol = 2,
          labels = paste0(LETTERS[8], seq(1,100)))
```

#### 相位角 {#delta_p_ob_filtered_wepa .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_2") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_2")],
          ncol = 2,
          labels = paste0(LETTERS[8], seq(which(myplot_table_global_filter[["block"]] == "t0_2") %>% min(),1000)))
```

#### 體水份 {#delta_p_ob_filtered_water .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_3") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_3")],
          ncol = 2,
          labels = paste0(LETTERS[8], seq(which(myplot_table_global_filter[["block"]] == "t0_3") %>% min(),1000)))
```

#### inbody - 部位別 {#delta_p_ob_filtered_inbody_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_4") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_4")],
          ncol = 2,
          labels = paste0(LETTERS[8], seq(which(myplot_table_global_filter[["block"]] == "t0_4") %>% min(),1000)))
```

#### 體水份 - 部位別 {#delta_p_ob_filtered_water_part .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_5") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_5")],
          ncol = 2,
          labels = paste0(LETTERS[8], seq(which(myplot_table_global_filter[["block"]] == "t0_5") %>% min(),1000)))
```

#### Glucose/Insulin {#delta_p_ob_filtered_gi .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_6") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_6")],
          ncol = 2,
          labels = paste0(LETTERS[9], seq(which(myplot_table_global_filter[["block"]] == "t0_6") %>% min(),1000)))
```

#### Lipid {#delta_p_ob_filtered_lipid .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_7") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_7")],
          ncol = 2,
          labels = paste0(LETTERS[9], seq(which(myplot_table_global_filter[["block"]] == "t0_7") %>% min(),1000)))
```

#### Kidney {#delta_p_ob_filtered_kidney .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_8") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_8")],
          ncol = 2,
          labels = paste0(LETTERS[9], seq(which(myplot_table_global_filter[["block"]] == "t0_8") %>% min(),1000)))
```

#### Hormone {#delta_p_ob_filtered_hormone .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_9") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_9")],
          ncol = 2,
          labels = paste0(LETTERS[9], seq(which(myplot_table_global_filter[["block"]] == "t0_9") %>% min(),1000)))
```

#### Hematology {#delta_p_ob_filtered_hematology .unnumbered}

```{r, results='asis', fig.dim = c(5*2,4*(sum(myplot_table_global_filter[["block"]] == "delta_p_10") %>% divide_by(2) %>% ceiling()))}
plot_grid(plotlist = myplots_exclude_record_factor[which(myplot_table_global_filter[["block"]] == "delta_p_10")],
          ncol = 2,
          labels = paste0(LETTERS[9], seq(which(myplot_table_global_filter[["block"]] == "t0_10") %>% min(),1000)))
```

### Summary {#Summary_ob_filtered .unnumbered}



```{r, results='asis',  paged.print=TRUE}
table_02_exclude_record_factor
```